\documentclass[main.tex]{subfiles}
\begin{document}

No journey is undertaken alone, and this thesis—like the road to Mordor—would not have been possible without the guidance, companionship, and courage of many.

First and foremost, I thank my advisor, Mithrandir, known to most as Gandalf, for his unwavering wisdom, timely interventions, and for believing in me even when I doubted myself. His counsel has lit the darkest paths.

To Samwise Gamgee, whose loyalty and resilience carried me farther than any algorithm or theory ever could—thank you. This work is as much yours as it is mine.

To the Fellowship—Aragorn, Legolas, Gimli, Boromir, Merry, and Pippin—your camaraderie in the face of uncertainty taught me the value of collaboration and courage. Your strength and perspective shaped every chapter of this work.

To Elrond and the scholars of Rivendell, thank you for providing a safe place of learning and deep archives from which this thesis drew its earliest insights.

To Lady Galadriel, for reminding me that even the smallest light can pierce the greatest darkness.

To Gollum—though your intentions were ever conflicted, your presence reminded me of the complexity of the paths we must all choose, and of the hidden cost in every shortcut.

Lastly, I thank the people of the Shire. Though distant from the world of academia, your simple joys and steadfast hearts remained my reason to finish what was begun.

The road went ever on, but I could not have walked it alone.

The text in this humorous template was generated with ChatGPT\@. If you have any improvements or want to actually write Frodo's thesis, please submit a PR\@.

\end{document}
